Joint photometric modeling for improved measurements in imaging surveys.

### 2014-11-14 documents/paper/ms_v0.0.tex
fig text

>>>>

\begin{figure}
\centering
\includegraphics[clip=true, trim=1.5cm 0.5cm 1.5cm 0.5cm,
  width=16cm]{fig1.png}
\caption{Shown are three different projections of one tenth of the DR10
photometric data used (black points), with the top/bottom row corresponding
objects classified as stars/galaxies (\ttt{type} $=6, 3$).  Gray contours
indicate the different XD components.  For the top we only plot the
$N_{\rm point}$ components while in the bottom we plot the rest.  Note,
however, when we compute our model we do not use SDSS classifications -- all
data is modeled with the combination of both top and bottom contours.  Note
the components modeling psfmag minus modelmag for starlike objects prefer
small variance, and generally the model follows the data well.
}
\label{fig:contours}
\end{figure}
